Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-12 paper.qmd
Add description for binning data

Points are allocated to the bin that they fall in by considering the nearest centroid.

>>>>

Points are allocated to the bin they fall into based on the nearest centroid. In situations where a point is equidistant from multiple centroids, tie-breaking rules are applied. If multiple centroids are in the same row, the point is assigned to the leftmost centroid. If multiple centroids are in different rows, the point is assigned to the bottom centroid.
